---
title: "R Introduction - Exercises"
name: "Please fill"
date: "Please add"
format: html
editor: source
---

Fill in the exercises the code.
Ensure that the script runs in full and push to your repository.

### Exercise 1
1. Create a vector of the letters A, B and C.

```{r}
# Your answer here
```


2. Assign the vector to the variable `my_letters`.

```{r}
# Your answer here
```


3. Check the what happens when you run letters (just this) on the command line.

```{r}
# Your answer here
```


4. What happens when you concatenate two vectors? Use `my_letters` twice

```{r}
# Your answer here
```


5. Add the number 1 to letters. What happens to the type of the vector?

```{r}
# Your answer here
```


### Exercise 2


1. Create a vector `my_vec` with the numbers from 1 through 8.

```{r}
# Your answer here
```

2. Apply the operation `+2` to the vector/
```{r}
# Your answer here
```

3. Add the vector containing 1, 2, 3, 4 to my_vec. What do you observe?

```{r}
# Your answer here
```

### Exercise 3


1.  Consider the R output of the matrix below:
```
   [,1] [,2]
   [1,]    4    1
   [2,]    9    5
   [3,]   10    7
```
1. What was one of the correct commands used to write this matrix?
```{r}
# Your answer here
```

  
2. Assign the matrix as `A`
```{r}
# Your answer here
```
  
3. Check the dimensions
```{r}
# Your answer here
```
  
4. Extract the element `5`
```{r}
# Your answer here
```
  
5. Add the vector `c(0,0,0)` as a new column and update `A`
```{r}
# Your answer here
```

6. Modify the element 4 to `0`
```{r}
# Your answer here
```
  
7. Compute the transpose of `A`
```{r}
# Your answer here
```


### Exercise 4

1. Create a function that sums up two values even if provided as characters values

```{r}
# Your answer here
```


### Exercise 5

1. Create a function that returns the mean, median and standard deviation


### Exercise 6
1. Create a pipe statement that counts the number of NAs in vector.
The output of `c('1' , "a", NA, "2", NA)` should be 2.
